Figures from: Vertebrate host availability and the thermal properties of mosquito-borne parasite transmission

### 2023-05-12 manuscript-figures.Rmd
little fixes

# Tell R where the manuscript lives
here::i_am("manuscript-figures.Rmd")

@@

data.in.transform <- read_rds("data/clean/TPC_param_samples.rds")
# Define temperature range of study
Temps <- seq(10, 40, length.out = 601) # full: length.out = 601, thin: length.out = 301

@@

plot_bool = FALSE
source("code/trait-transform.R")
# Host density vector: Number of values to include to consider for vertebrate host density
KH_vec_length <- 300 # full = 300, thin = 20

@@

source("code/trait-variation.R")

# Load output data -------------------------------------------------------------

# R0 data
data.R0 <- read_rds("results/R0_vals.rds")
# Topt data
data.Topt <- read_rds("results/Topt_vals.rds")
# Critical thermal extrema data
data.CT <- read_rds("results/CT_vals.rds")

@@

@@

```{r fig-1_contact_comparison, dev = c('pdf','svg', 'tiff'), out.width='100%', fig.align='center', fig.height=5, fig.width=7, fig.align='center', fig.cap='\\label{fig:contact_comparison} A comparison of the Ross-Macdonald and Chitnis contact rate formulations.'}

@@

```{r fig-3_MosquitoThermalTraits, dev = c('pdf','svg', 'tiff'),  out.width='100%', fig.height=6, fig.width=9, fig.align='center', fig.cap='\\label{fig:MosquitoThermalTraits} Thermal performance curves for the mosquito and parasite traits used in our model. '}

## Set up plot dataframe
MosqThermTraits_df <- mean.Vec %>%
  ## Set up plot dataframe
  # Mortality rate
  mutate(muV = 1/lf) %>% 
  # Recruitment rate
  mutate(lambdaV = V0 * muV) %>%
  # Prob. of surviving EIP
  mutate(P_EIP = exp(-muV / etaV)) %>%
  # Select relevant traits and parameters
  select(
    Temperature, system_ID, lambdaV, sigmaV, betaV, lf, P_EIP
  ) %>%
  # Turn all columns except Temperature and system_ID (Mosquito sp. + parasite sp.) into
  # 'variables'
  melt(id = c("Temperature", "system_ID")) %>%
  group_by(Temperature, system_ID)

@@

```{r fig-4_R0_TPCs, dev = c('pdf','svg', 'tiff'),  message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:R0_plots} ${R}_0$ as a function of temperature has the properties of a thermal performance curve (TPC): it is positive on a single bounded interval and has a unique maximum value.'}

@@

```{r fig-5_Topt, dev = c('pdf','svg', 'tiff'), dev="cairo_pdf", message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:Topt} The thermal optimum for transmission, $T_{opt}$, may be sensitive to vertebrate host population density and biting tolerance.'}
# Shows how the transmission thermal optimum depends on vertebrate host availability (density and biting tolerance) in each of the systems we consider.

@@

```{r fig-6_CT_Width, dev = c('pdf','svg', 'tiff'), dev="cairo_pdf", message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CT_Width} The parasite population thermal tolerance range, the range of temperatures at which parasite transmission is expected to persist, is widest when biting tolerance is high and vertebrate host population density is low.'}
# Shows how the parasite thermal niche (temperatures between CT_min and CT_max) 
# depends on vertebrate host availability (density and biting tolerance) in each
# of the focal systems.

@@

CTwidth_df <- data.CT %>%
  filter(variable == "CTwidth") %>% 
  mutate(sigmaH_proxy = sigmaH) %>% 
  # Arrange along the plotting variables
  arrange(system_ID, KH, sigmaH_proxy, mean) %>% 
  ungroup()

infinite_skew <- 10^3 + 250
CTwidth_df <- inf_skew_func(CTwidth_df, infinite_skew, divide_order = 3, 8)

infinite_divide <- 10^mean(c(2, log10(infinite_skew)))
CTWidth_heat_plots <- CTwidth_df %>%
  ## Set up plot ##
  # x = biting tolerance (with a point at infinity),
  # y = vertebrate host population density,
  # color = width of parasite thermal mean_CTwidth
  ggplot(aes(x = KH, y = sigmaH_proxy, z = mean)) +
  # CTwidth for FINITE sigmaH:
  geom_contour_filled(data = filter(CTwidth_df, sigmaH_proxy < infinite_divide**0.99)) +
  # CTwidth for INFINITE sigmaH:
  geom_contour_filled(data = filter(CTwidth_df, sigmaH_proxy > infinite_divide**1.01)) +
  # x-axis: log10-scale with no buffer space
  scale_x_log10(
    name = TeX("Vertebrate host population density (ind/ha)"),
    expand = c(0, 0),
    limits = c(0.05, 1E4),
    breaks = 10^seq(-1, 4, 1),
    labels = TeX(c("$0.1$", "$1$", "$10", "$100$", "$10^3$", "$10^4$"))
  ) +
  # y-axis: log10-scale y axis, with no buffer space
  scale_y_log10(
    name = TeX("Biting tolerance (bites per host per day)"),
    expand = c(0, 0),
    breaks = sigmaH_breaks,
    labels = sigmaH_labels
  ) +
  # color:
  scale_fill_viridis_d(
    name = "Mean parasite\nthermal tolerance\nrange width (°C)",
    option = "plasma"
  ) +
  # faceting:
  facet_wrap(~system_ID, scales = "free", nrow = 2, labeller = labeller()) +
  # legend:
  guides(fill = guide_coloursteps(
    title.position = "top", title.hjust = 0.5,
    barwidth = unit(5, "cm"),
    show.limits = TRUE
  )) +
  # theme options:
  theme_minimal(16) +
  theme(
    legend.box = "horizontal",
    legend.position = "bottom",
    legend.margin = margin(0, 0, 0, 0),
    legend.title = element_text(size = 10),
    legend.direction = "horizontal",
    legend.justification = "left",
    axis.title.x = element_text(hjust = 0.5),
    strip.text = ggtext::element_markdown(
      size = 11,
      hjust = 0,
      padding = margin(0, 0, 0, 0),
      margin = margin(1, 1, 1, 1)
    )
  )

@@

# Supplementary Figures

```{r fig-S1_R0_heatmap_plots_all, dev = c('pdf','svg', 'tiff'), message=FALSE, out.width='100%', fig.width=9, fig.height=11, fig.align='center', fig.cap='\\label{fig:R0_heatmap_plots_all} R0 heatmap expressing threshold (R0 = 1) as a contour and thermal optimum as ridges.'}
# Plot R0 vs. temperature and biting tolerance (sigmaH). One panel each for low, mid, high vert host pop density.

# x = vertebrate host biting tolerance (needs to vary from "zero" to "infinity")
# y = Temperature
# color = R0
# curves:
#   R0 = 1 contour (black curve)
#   Topt (red curve)

# Facets:
# Rows = levels of vertebrate host population density
# Columns = two MBPT systems
# Total = 6 plots

## Set up plot data frame
# We re-create the output data frame so that we can vary sigmaH correctly.
# We also drop the resolution of KH down to just three values
# Need to update functions so that sigmaH == Inf <~> Model == "Ross-Macdonald"

## Configure data frame for plotting
R0_df <- AllOutputs %>%
  select(system_ID, system_label, Temperature, sigmaH, KH, R0) %>%
  # Consider only 3 values of KH (on a log10-scale)
  filter(KH %in% c(1E-1, 1E0, 1E1)) %>%
  # Choose a limited range of sigmaH values
  filter(sigmaH > 10^0.5) %>%
  # Group by plotting variables
  group_by(system_ID, KH, sigmaH) %>%
  # Calculate Topt (which.max requires grouping)
  mutate(Topt = `Temperature`[which.max(R0)]) %>%
  as_tibble() %>%
  arrange(system_ID, sigmaH, Temperature)

## Add a "point at infinity" for sigmaH
# Value of sigmaH to replace 'Inf' with for plotting
infinite_skew <- 10^3 + 2500

# Get the largest value of log10(sigmaH)
max_log10sigmaH <- filter(R0_df, is.finite(sigmaH)) %>%
  select(sigmaH) %>%
  max() %>%
  log10()

# Used to create a gap dividing finite and infinite sigmaH
infinite_divide <- 10^mean(c(3, log10(infinite_skew)))

# add a second proxy sigmaH point at infinity to make the values easier to see there
temp <- filter(R0_df, is.infinite(sigmaH)) %>%
  mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH, 1.2 * infinite_divide))
# Create a proxy sigmaH variable that replaces Inf with infinite_skew
R0_df <- mutate(R0_df, sigmaH_proxy = ifelse(is.finite(sigmaH),
                                             sigmaH, infinite_skew
))
R0_df <- add_row(R0_df, temp) %>% distinct()

## Compute mosquito thermal tolerance range (minimum and maximum)
temp_MosqThermRange_df <- MosqThermRange_df %>%
  select(system_label, CTmin_V0, CTmax_V0)

## PLOTTING ##

## Options
# Define sigmaH tick breaks and labels
sigmaH_breaks <- c(10^c(seq(-1, 3, by = 1)), infinite_divide, infinite_skew)
sigmaH_labels <- c(paste(c(10^c(seq(-1, 3, by = 1)))), TeX("$\\ldots$"), TeX("$\\infty$"))

# Labels for facet rows
R0_df$KH <- factor(R0_df$KH, levels = c(.1, 1, 10))
mylabels <- as_labeller(c(
  `0.1` = "0.1 vertebrate hosts / ha",
  `1` = "1 vertebrate host / ha",
  `10` = "10 vertebrate hosts / ha"
))

# Breaks used to decide fill for the heat map
fill_breaks <- c(1, seq(5, 20, by = 5), Inf)

# Define colors for heat map so that values of R0>1 go from yellow to red
my.cols <- rev(c(rev(brewer.pal(length(fill_breaks) - 1, "YlOrRd"))))

## PLOT ##
R0_plot <- R0_df %>%
  ggplot(mapping = aes(x = sigmaH_proxy, y = Temperature, z = R0)) +

  # Mosquito thermal tolerance range lines
  geom_hline(
    data = temp_MosqThermRange_df,
    aes(yintercept = CTmin_V0, colour = "VTTR"),
    lwd = 1.275
  ) +
  geom_hline(
    data = temp_MosqThermRange_df,
    aes(yintercept = CTmax_V0, colour = "VTTR"),
    lwd = 1.275
  ) +

  # R0 contours for FINITE sigmaH:
  geom_contour_filled(
    data = filter(R0_df, sigmaH_proxy < infinite_divide**0.98),
    breaks = fill_breaks
  ) +

  # R0 contours for INFINITE sigmaH:
  geom_contour_filled(
    data = filter(R0_df, sigmaH_proxy > infinite_divide**1.02),
    breaks = fill_breaks
  ) +

  # R0 = 1 contour:
  geom_contour(aes(colour = "R0=1"), breaks = c(1), size = 1) +

  # Topt curve:
  geom_line(
    # data = filter(R0_df, R0>1), # uncomment to only display Topt when R0 exceeds one
    mapping = aes(
      x = sigmaH_proxy,
      y = Topt,
      colour = "Topt"
    ),
    lwd = 1,
    linetype = 1
  ) +

  # white lines breaking up finite/infinite sigmaH values
  geom_vline(
    aes(xintercept = 0.85 * infinite_divide),
    colour = "white",
    lwd = .8,
    show.legend = FALSE
  ) +
  geom_vline(
    aes(xintercept = infinite_divide),
    colour = "white",
    lwd = .8,
    show.legend = FALSE
  ) +
  geom_vline(
    aes(xintercept = 1.2 * infinite_divide),
    colour = "white",
    lwd = .8,
    show.legend = FALSE
  ) +

  # x-axis:
  scale_x_log10(
    name = TeX("Vertebrate host biting tolerance (bites per host per day)"),
    breaks = sigmaH_breaks,
    labels = sigmaH_labels,
    expand = c(0, 0)
  ) +

  # y-axis:
  scale_y_continuous(
    name = expression("Temperature "(degree * C)),
    expand = c(0, 0),
    limits = c(14, 36),
    breaks = seq(10, 36, by = 2)
  ) +

  # color:
  scale_colour_manual(
    name = "",
    labels = c(
      "R0=1" = unname(TeX("$R_0=1$")),
      "Topt" = "Transmission\nthermal\noptimum",
      "VTTR" = "Mosquito\nthermal\ntolerance\nlimit"
    ),
    values = c("black", "purple", "grey"),
    guide = guide_legend(
      order = 1,
      keyheight = unit(2, "cm"),
      override.aes = list(size = 6)
    )
  ) +

  # fill:
  scale_fill_manual(
    name = TeX("$R_0$"),
    values = my.cols,
    guide = guide_colorsteps(
      order = 2,
      breaks = fill_breaks,
      barheight = unit(8, "cm")
    )
  ) +

  # faceting:
  facet_rep_grid(
    rows = vars(system_label),
    cols = vars(KH),
    scales = "free_y",
    labeller = labeller(.cols = mylabels),
    repeat.tick.labels = "left"
  ) +

  # theme options:
  theme_minimal_hgrid(11) +
  theme(
    axis.line = element_line(),
    panel.spacing = unit(1, "lines"),
    legend.text = element_text(size = 11),
    legend.text.align = 0,
    strip.text = ggtext::element_markdown(
      size = 8,
      hjust = 0
    )
  )

# Plot it
R0_plot
```

```{r fig-S2_Topt_plots_varyKH, dev = c('pdf','svg', 'tiff'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:Topt_plots_varyKH} The thermal optimum for transmission, $T_{opt}$, may be sensitive to vertebrate host population density and biting tolerance.'}

Topt_df <- ThermPathChars %>%
  filter(KH > 0.01) %>%
  filter(sigmaH %in% 10^seq(0, 2) | is.infinite(sigmaH)) %>%
  group_by(KH) %>%
  # Arrange along the plotting variables
  arrange(system_ID, KH, Topt) %>%
  arrange(sigmaH) %>%
  ungroup()

Topt_plots <- Topt_df %>%
  ## Set up plot ##
  # x = blood meal supply, y = thermal optimum,
  # color = sigmaH
  ggplot(aes(
    x = KH, y = Topt,
    colour = as.factor(sigmaH)
  )) +

  # Topt curves:
  geom_path(lwd = 1) +

  # x-axis: log10 scale, no buffer space
  scale_x_log10(
    name = TeX("Vertebrate host population density (ind/ha)"),
    expand = c(0, 0),
    limits = c(0.01, 2E4),
    breaks = 10^seq(-2, 4),
    labels = TeX(c(
      "0.01", "0.1", "$1$", "$10$", "$100$", "$10^3$", "$10^4$"
    ))
  ) +

  # y-axis
  scale_y_continuous(
    name = expression("Thermal optimum "(degree * C)),
    expand = c(0.05, 0.05),
    limits = range(ThermPathChars$Topt),
    breaks = seq(floor(range(ThermPathChars$Topt)[1]),
                 floor(range(ThermPathChars$Topt)[2]),
                 by = 1
    )
  ) +
  # color:
  scale_colour_manual(
    name = "Vertebrate host biting tolerance\n(bites per host per day)",
    values = c(met.brewer("VanGogh3", 3, direction = 1), "black"),
    # values = c(brewer.pal(9, "YlOrRd")[c(3, 5, 7)], "black"),
    breaks = c(1, 10, 100, Inf),
    labels = unname(c("1 (Chitnis)", "10 (Chitnis)", "100 (Chitnis)", TeX("$\\infty$ (Ross-Macdonald)")))
  ) +

  # faceting:
  facet_wrap(~system_label,
             scales = "free",
             nrow = 2,
             labeller = labeller()
  ) +

  # theme options:
  theme_minimal_hgrid(11) +
  guides(color = guide_legend(override.aes = list(size = 4))) +
  theme(
    legend.position = "bottom",
    legend.margin = margin(),
    legend.direction = "vertical",
    legend.title = element_text(size = 10),
    legend.text = element_text(
      size = 10,
      hjust = 0
    ),
    legend.justification = "left",
    axis.title.x = element_text(hjust = 0.5),
    strip.text = ggtext::element_markdown(
      size = 11,
      hjust = 0,
      padding = margin(0, 0, 0, 0),
      margin = margin(1, 1, 1, 1)
    )
  )

# Plot
shift_legend(Topt_plots)

```{r fig-S3_Topt_plots, dev = c('pdf','svg', 'tiff'), message=FALSE, out.width='100%', fig.width=9, fig.height=8, fig.align='center', fig.cap='\\label{fig:Topt_plots} Transmission thermal optimum as a function of vertebrate host availability.'}

# x-axis = vertebrate host biting tolerance
# y-axis = thermal optimum
# color = vertebrate host population density

Topt_df <- ThermPathChars %>%
  # Choose appropriate pop. dens. values and group
  filter(KH %in% 10^seq(0, 4)) %>%
  group_by(KH) %>%
  # Arrange along the plotting variables
  arrange(system_ID, sigmaH, Topt) %>%
  arrange(KH) %>%
  ungroup()

Topt_plots <- Topt_df %>%
  ## Set up plot ##
  # x-axis = vertebrate host biting tolerance, y-axis = thermal optimum,
  # color = vertebrate host population density
  ggplot(aes(x = sigmaH_proxy, y = Topt, colour = as.factor(KH))) +

  # Topt curves:
  geom_path(lwd = 2) +

>>>>

# Tell R where the manuscript lives
# here::i_am("manuscript-figures.Rmd")

data.in.transform <- read_rds(here::here("data/clean/TPC_param_samples.rds"))

@@

# Define temperature range of study
Temps <- seq(10, 40, length.out = 601) # full: length.out = 601, thin: length.out = 301

@@

plot_bool = FALSE
source("code/trait-transform.R", local = TRUE)
# Host density vector: Number of values to include to consider for vertebrate host density
KH_vec_length <- 300 # full = 300, thin = 20

@@

# Get data for plotting thermal performance curves (data.Vec)
source("code/trait-variation.R", local = TRUE)

# Load output data -------------------------------------------------------------
# These data are produced by the code in code/get-outputs.R

# R0 data
data.R0 <- read_rds("results/R0_vals.rds") # !!! needs to be updated to include 1e-1, 1e0, 1e1
# Topt data
data.Topt <- read_rds("results/Topt_vals.rds")
# Critical thermal extrema data
data.CT <- read_rds("results/CT_vals.rds")

@@

median.Vec <- data.Vec %>% 
  select(-c(mosquito_species, pathogen, muL, etaL)) %>% 
  pivot_longer(cols = lf:V0, names_to = "variable", values_to = "value") %>%
  group_by(system_ID, Temperature, variable) %>% 
  summarise(median = median(value), .groups = "keep") %>% 
  ungroup() %>% 
  pivot_wider(names_from = "variable", values_from = "median") %>% 
  mutate(etaL = rhoL / (deltaL + eps)) %>%
  # Aquatic-stage mosquito mortality rate. This should be ~infinite if deltaL = 0
  mutate(muL = etaL - rhoL) %>%
  mutate(V0 = ifelse( sigmaV_f * deltaL < (1 / lf),
                      0,
                      KL * rhoL * lf * (1 - 1 / (lf * sigmaV_f * deltaL))))

@@

```{r fig-1_contact_comparison, dev = c('pdf','svg', 'png'), out.width='100%', fig.align='center', fig.height=5, fig.width=7, fig.align='center', fig.cap='\\label{fig:contact_comparison} A comparison of the Ross-Macdonald and Chitnis contact rate formulations.'}

@@

```{r fig-3_MosquitoThermalTraits, dev = c('pdf','svg', 'png'),  out.width='100%', fig.height=6, fig.width=9, fig.align='center', fig.cap='\\label{fig:MosquitoThermalTraits} Thermal performance curves for the mosquito and parasite traits used in our model. '}

## Set up plot dataframe
MosqThermTraits_df <- median.Vec %>%
  ## Set up plot dataframe
  # Mortality rate
  mutate(muV = 1/lf) %>% 
  # Recruitment rate
  mutate(lambdaV = V0 * muV) %>%
  # Prob. of surviving EIP
  mutate(P_EIP = exp(-muV / etaV)) %>%
  # Select relevant traits and parameters
  select(
    Temperature, system_ID, lambdaV, sigmaV, betaV, lf, P_EIP
  ) %>%
  # Turn all columns except Temperature and system_ID (Mosquito sp. + parasite sp.) into
  # 'variables'
  melt(id = c("Temperature", "system_ID")) %>%
  group_by(Temperature, system_ID)

@@

```{r fig-4_R0_TPCs, dev = c('pdf','svg', 'png'),  message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:R0_plots} ${R}_0$ as a function of temperature has the properties of a thermal performance curve (TPC): it is positive on a single bounded interval and has a unique maximum value.'}

@@

```{r fig-5_Topt, dev = c('pdf','svg', 'png'), dev="cairo_pdf", message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:Topt} The thermal optimum for transmission, $T_{opt}$, may be sensitive to vertebrate host population density and biting tolerance.'}
# Shows how the transmission thermal optimum depends on vertebrate host availability (density and biting tolerance) in each of the systems we consider.

@@

```{r fig-6_CT_Width, dev = c('pdf','svg', 'png'), dev="cairo_pdf", message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CT_Width} The parasite population thermal tolerance range, the range of temperatures at which parasite transmission is expected to persist, is widest when biting tolerance is high and vertebrate host population density is low.'}
# Shows how the parasite thermal niche (temperatures between CT_min and CT_max) 
# depends on vertebrate host availability (density and biting tolerance) in each
# of the focal systems.

@@

CTwidth_df <- data.CT %>%
  filter(variable == "CTwidth") %>% 
  mutate(sigmaH_proxy = sigmaH) %>% 
  # Arrange along the plotting variables
  arrange(system_ID, KH, sigmaH_proxy, median) %>% 
  ungroup()

CTwidth_df <- inf_skew_func(CTwidth_df, infinite_skew, infinite_divide, 8)

CTWidth_heat_plots <- CTwidth_df %>%
  ## Set up plot ##
  # x = biting tolerance (with a point at infinity),
  # y = vertebrate host population density,
  # color = width of parasite thermal mean_CTwidth
  ggplot(aes(x = KH, y = sigmaH_proxy, z = mean)) +
  # CTwidth for FINITE sigmaH:
  geom_contour_filled(data = filter(CTwidth_df, sigmaH_proxy < infinite_divide**0.99)) +
  # CTwidth for INFINITE sigmaH:
  geom_contour_filled(data = filter(CTwidth_df, sigmaH_proxy > infinite_divide**1.01)) +
  # x-axis: log10-scale with no buffer space
  scale_x_log10(
    name = TeX("Vertebrate host population density (ind/ha)"),
    expand = c(0, 0),
    limits = c(0.05, 1E4),
    breaks = 10^seq(-1, 4, 1),
    labels = TeX(c("$0.1$", "$1$", "$10", "$100$", "$10^3$", "$10^4$"))
  ) +
  # y-axis: log10-scale y axis, with no buffer space
  scale_y_log10(
    name = TeX("Biting tolerance (bites per host per day)"),
    expand = c(0, 0),
    breaks = sigmaH_breaks,
    labels = sigmaH_labels
  ) +
  # color:
  scale_fill_viridis_d(
    name = "Median parasite\nthermal tolerance\nrange width (°C)",
    option = "plasma"
  ) +
  # faceting:
  facet_wrap(~system_ID, scales = "free", nrow = 2, labeller = labeller()) +
  # legend:
  guides(fill = guide_coloursteps(
    title.position = "top", title.hjust = 0.5,
    barwidth = unit(5, "cm"),
    show.limits = TRUE
  )) +
  # theme options:
  theme_minimal(16) +
  theme(
    legend.box = "horizontal",
    legend.position = "bottom",
    legend.margin = margin(0, 0, 0, 0),
    legend.title = element_text(size = 10),
    legend.direction = "horizontal",
    legend.justification = "left",
    axis.title.x = element_text(hjust = 0.5),
    strip.text = ggtext::element_markdown(
      size = 11,
      hjust = 0,
      padding = margin(0, 0, 0, 0),
      margin = margin(1, 1, 1, 1)
    )
  )

@@

<!-- # Supplementary Figures -->

<!-- ```{r fig-S1_R0_heatmap_plots_all, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=11, fig.align='center', fig.cap='\\label{fig:R0_heatmap_plots_all} R0 heatmap expressing threshold (R0 = 1) as a contour and thermal optimum as ridges.'} -->
<!-- # Plot R0 vs. temperature and biting tolerance (sigmaH). One panel each for low, mid, high vert host pop density. -->

<!-- # x = vertebrate host biting tolerance (needs to vary from "zero" to "infinity") -->
<!-- # y = Temperature -->
<!-- # color = R0 -->
<!-- # curves: -->
<!-- #   R0 = 1 contour (black curve) -->
<!-- #   Topt (red curve) -->

<!-- # Facets: -->
<!-- # Rows = levels of vertebrate host population density -->
<!-- # Columns = two MBPT systems -->
<!-- # Total = 6 plots -->

<!-- ## Set up plot data frame -->
<!-- # We re-create the output data frame so that we can vary sigmaH correctly. -->
<!-- # We also drop the resolution of KH down to just three values -->
<!-- # Need to update functions so that sigmaH == Inf <~> Model == "Ross-Macdonald" -->

<!-- ## Configure data frame for plotting -->
<!-- R0_df <- data.R0 %>% -->
<!--   select(system_ID, system_label, Temperature, sigmaH, KH, median) %>% -->
<!--   rename(R0 = median) %>%  -->
<!--   # Consider only 3 values of KH (on a log10-scale) -->
<!--   filter(KH %in% c(1E-1, unique(data.R0$KH)[7], unique(data.R0$KH)[10])) %>% # !!! temporary. recalculate R0 with 1e-1, 1e0, 1e1 -->
<!--   # Choose a limited range of sigmaH values -->
<!--   filter(sigmaH > 10^0.5) %>% -->
<!--   # Group by plotting variables -->
<!--   group_by(system_ID, KH, sigmaH) %>% -->
<!--   # Calculate Topt (which.max requires grouping) -->
<!--   mutate(Topt = `Temperature`[which.max(R0)]) %>% -->
<!--   as_tibble() %>% -->
<!--   arrange(system_ID, sigmaH, Temperature) -->

<!-- ## Add a "point at infinity" for sigmaH -->
<!-- # Value of sigmaH to replace 'Inf' with for plotting -->
<!-- infinite_skew <- 10^3 + 2500 -->

<!-- # Get the largest value of log10(sigmaH) -->
<!-- max_log10sigmaH <- filter(R0_df, is.finite(sigmaH)) %>% -->
<!--   select(sigmaH) %>% -->
<!--   max() %>% -->
<!--   log10() -->

<!-- # Used to create a gap dividing finite and infinite sigmaH -->
<!-- infinite_divide <- 10^mean(c(3, log10(infinite_skew))) -->

<!-- # add a second proxy sigmaH point at infinity to make the values easier to see there -->
<!-- temp <- filter(R0_df, is.infinite(sigmaH)) %>% -->
<!--   mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH, 1.2 * infinite_divide)) -->
<!-- # Create a proxy sigmaH variable that replaces Inf with infinite_skew -->
<!-- R0_df <- mutate(R0_df, sigmaH_proxy = ifelse(is.finite(sigmaH), -->
<!--                                              sigmaH, infinite_skew -->
<!-- )) -->
<!-- R0_df <- add_row(R0_df, temp) %>% distinct() -->

<!-- ## Compute mosquito thermal tolerance range (minimum and maximum) -->
<!-- temp_MosqThermRange_df <- MosqThermRange_df %>% -->
<!--   select(system_label, CTmin_V0, CTmax_V0) -->

<!-- ## PLOTTING ## -->

<!-- ## Options -->
<!-- # Define sigmaH tick breaks and labels -->
<!-- sigmaH_breaks <- c(10^c(seq(-1, 3, by = 1)), infinite_divide, infinite_skew) -->
<!-- sigmaH_labels <- c(paste(c(10^c(seq(-1, 3, by = 1)))), TeX("$\\ldots$"), TeX("$\\infty$")) -->

<!-- # Labels for facet rows -->
<!-- R0_df$KH <- factor(R0_df$KH, levels = c(.1, 1, 10)) -->
<!-- mylabels <- as_labeller(c( -->
<!--   `0.1` = "0.1 vertebrate hosts / ha", -->
<!--   `1` = "1 vertebrate host / ha", -->
<!--   `10` = "10 vertebrate hosts / ha" -->
<!-- )) -->

<!-- # Breaks used to decide fill for the heat map -->
<!-- fill_breaks <- c(1, seq(5, 20, by = 5), Inf) -->

<!-- # Define colors for heat map so that values of R0>1 go from yellow to red -->
<!-- my.cols <- rev(c(rev(brewer.pal(length(fill_breaks) - 1, "YlOrRd")))) -->

<!-- ## PLOT ## -->
<!-- R0_plot <- R0_df %>% -->
<!--   ggplot(mapping = aes(x = sigmaH_proxy, y = Temperature, z = R0)) + -->

<!--   # Mosquito thermal tolerance range lines -->
<!--   geom_hline( -->
<!--     data = temp_MosqThermRange_df, -->
<!--     aes(yintercept = CTmin_V0, colour = "VTTR"), -->
<!--     lwd = 1.275 -->
<!--   ) + -->
<!--   geom_hline( -->
<!--     data = temp_MosqThermRange_df, -->
<!--     aes(yintercept = CTmax_V0, colour = "VTTR"), -->
<!--     lwd = 1.275 -->
<!--   ) + -->

<!--   # R0 contours for FINITE sigmaH: -->
<!--   geom_contour_filled( -->
<!--     data = filter(R0_df, sigmaH_proxy < infinite_divide**0.98), -->
<!--     breaks = fill_breaks -->
<!--   ) + -->

<!--   # R0 contours for INFINITE sigmaH: -->
<!--   geom_contour_filled( -->
<!--     data = filter(R0_df, sigmaH_proxy > infinite_divide**1.02), -->
<!--     breaks = fill_breaks -->
<!--   ) + -->

<!--   # R0 = 1 contour: -->
<!--   geom_contour(aes(colour = "R0=1"), breaks = c(1), size = 1) + -->

<!--   # Topt curve: -->
<!--   geom_line( -->
<!--     # data = filter(R0_df, R0>1), # uncomment to only display Topt when R0 exceeds one -->
<!--     mapping = aes( -->
<!--       x = sigmaH_proxy, -->
<!--       y = Topt, -->
<!--       colour = "Topt" -->
<!--     ), -->
<!--     lwd = 1, -->
<!--     linetype = 1 -->
<!--   ) + -->

<!--   # white lines breaking up finite/infinite sigmaH values -->
<!--   geom_vline( -->
<!--     aes(xintercept = 0.85 * infinite_divide), -->
<!--     colour = "white", -->
<!--     lwd = .8, -->
<!--     show.legend = FALSE -->
<!--   ) + -->
<!--   geom_vline( -->
<!--     aes(xintercept = infinite_divide), -->
<!--     colour = "white", -->
<!--     lwd = .8, -->
<!--     show.legend = FALSE -->
<!--   ) + -->
<!--   geom_vline( -->
<!--     aes(xintercept = 1.2 * infinite_divide), -->
<!--     colour = "white", -->
<!--     lwd = .8, -->
<!--     show.legend = FALSE -->
<!--   ) + -->

<!--   # x-axis: -->
<!--   scale_x_log10( -->
<!--     name = TeX("Vertebrate host biting tolerance (bites per host per day)"), -->
<!--     breaks = sigmaH_breaks, -->
<!--     labels = sigmaH_labels, -->
<!--     expand = c(0, 0) -->
<!--   ) + -->

<!--   # y-axis: -->
<!--   scale_y_continuous( -->
<!--     name = expression("Temperature "(degree * C)), -->
<!--     expand = c(0, 0), -->
<!--     limits = c(14, 36), -->
<!--     breaks = seq(10, 36, by = 2) -->
<!--   ) + -->

<!--   # color: -->
<!--   scale_colour_manual( -->
<!--     name = "", -->
<!--     labels = c( -->
<!--       "R0=1" = unname(TeX("$R_0=1$")), -->
<!--       "Topt" = "Transmission\nthermal\noptimum", -->
<!--       "VTTR" = "Mosquito\nthermal\ntolerance\nlimit" -->
<!--     ), -->
<!--     values = c("black", "purple", "grey"), -->
<!--     guide = guide_legend( -->
<!--       order = 1, -->
<!--       keyheight = unit(2, "cm"), -->
<!--       override.aes = list(size = 6) -->
<!--     ) -->
<!--   ) + -->

<!--   # fill: -->
<!--   scale_fill_manual( -->
<!--     name = TeX("$R_0$"), -->
<!--     values = my.cols, -->
<!--     guide = guide_colorsteps( -->
<!--       order = 2, -->
<!--       breaks = fill_breaks, -->
<!--       barheight = unit(8, "cm") -->
<!--     ) -->
<!--   ) + -->

<!--   # faceting: -->
<!--   facet_rep_grid( -->
<!--     rows = vars(system_label), -->
<!--     cols = vars(KH), -->
<!--     scales = "free_y", -->
<!--     labeller = labeller(.cols = mylabels), -->
<!--     repeat.tick.labels = "left" -->
<!--   ) + -->

<!--   # theme options: -->
<!--   theme_minimal_hgrid(11) + -->
<!--   theme( -->
<!--     axis.line = element_line(), -->
<!--     panel.spacing = unit(1, "lines"), -->
<!--     legend.text = element_text(size = 11), -->
<!--     legend.text.align = 0, -->
<!--     strip.text = ggtext::element_markdown( -->
<!--       size = 8, -->
<!--       hjust = 0 -->
<!--     ) -->
<!--   ) -->

<!-- # Plot it -->
<!-- R0_plot -->
<!-- ``` -->

<!-- ```{r fig-S2_Topt_plots_varyKH, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:Topt_plots_varyKH} The thermal optimum for transmission, $T_{opt}$, may be sensitive to vertebrate host population density and biting tolerance.'} -->
<!-- Topt_df <- data.Topt %>%  -->
<!--   pivot_wider(id_cols = c("system_ID", "Model", "sigmaH", "KH"),  -->
<!--               names_from = variable, -->
<!--               values_from = c("mean", "median", "lowHCI", "highHCI"))  %>%  -->
<!--   right_join(read_rds("results/CT_vals.rds") %>%  -->
<!--                filter(variable == "CTwidth") %>%  -->
<!--                pivot_wider(id_cols = c("system_ID", "Model", "sigmaH", "KH"),  -->
<!--                            names_from = "variable", -->
<!--                            values_from = c("mean", "median", "lowHCI", "highHCI"))) %>%  -->
<!--   filter(sigmaH %in% c(1, 10, 100, Inf)) %>%  -->
<!--   # filter(mean_CTwidth>0) %>%  -->
<!--   select(-c(mean_CTwidth, median_CTwidth, lowHCI_CTwidth, highHCI_CTwidth)) %>% -->
<!--   rename(mean = mean_Topt, median = median_Topt, lowHCI = lowHCI_Topt,  -->
<!--          highHCI = highHCI_Topt) %>%  -->
<!--   # filter(KH > 0.01) %>% -->
<!--   # filter(sigmaH %in% 10^seq(0, 2) | is.infinite(sigmaH)) %>% -->
<!--   group_by(KH) %>% -->
<!--   # Arrange along the plotting variables -->
<!--   arrange(system_ID, KH, mean) %>% -->
<!--   arrange(sigmaH) %>% -->
<!--   ungroup() -->
